---
title: "MORDOR AMR spillover: 24 months, NP swabs"
author: "Ariktha Srivathsan"
format: 
  html:
    toc: true
    code-fold: true
    toc-depth: 3
    fig-width: 8
    fig-height: 6
editor:
  markdown:
    wrap: 72
execute:
  cache: true
  warning: false
---

```{r setup, include=FALSE}

rm(list = ls())

library(here)
```

```{r}
#| label: load data

source(here("R", "00-config.R"))
source(here("R", "00-functions.R"))

# Load NP data

perm_tx_int_raw <- readRDS(here("data", "output", "perm_tx_int.RDS"))

if(run_public){
  morb_grappe <- readRDS(file.path(path_data_clean, "morb_grappe.rds"))
  main_grappe <- readRDS(file.path(path_data_clean, "main_grappe.rds"))
  
  morb_tx_int <- readRDS(file.path(path_data_clean, "morb_tx_int.rds"))
  morb_rings <- readRDS(file.path(path_data_clean, "morb_rings.rds"))
  
  morb_gps <- readRDS(file.path(path_data_clean, "morb_gps.rds"))
  main_gps <- readRDS(file.path(path_data_clean, "main_gps.rds"))
  
  niger_shp <- readRDS(file.path(path_data_clean, "niger_shapefiles", "ner_admin2.shp"))
  
} else {
  morb_grappe <- readRDS(file.path(path_internal, "morb_grappe.rds"))
  main_grappe <- readRDS(file.path(path_internal, "main_grappe.rds"))
  
  morb_tx_int_raw <- readRDS(file.path(path_internal, "morb_tx_int.rds"))
  morb_rings_raw <- readRDS(file.path(path_internal, "morb_rings.rds"))
  
  morb_gps <- readRDS(file.path(path_internal, "morb_gps.rds"))
  main_gps <- readRDS(file.path(path_internal, "main_gps.rds"))
  
  np_dat <- readRDS(file.path(path_internal, "np_dat.rds"))
  
  niger_shp <- st_read(here("data", "untouched", "niger_shapefiles", "NER_admbnda_adm2_IGNN_20230720.shp"))
  
}

niger_shp <- niger_shp %>%
  mutate(mordor_states = ifelse(adm2_name %in% c("Falmey", "Boboye", "Loga"), TRUE, FALSE))


```

# NP data

```{r}
#| label: clean NP data

np_summ <- np_dat %>%
  group_by(phase, arm) %>%
  summarise(
    total_tested = sum(n_tested, na.rm = TRUE),
    total_grew = sum(n_grew, na.rm = TRUE),
    total_res = sum(n_res, na.rm = TRUE),
    n_na_res = sum(is.na(prop_res)),
    n = n()) %>%
  ungroup() %>%
  mutate(
    overall_prop_res = total_res / total_grew,
    overall_prop_res_test = total_res / total_tested
  )
    
```

## NP data summary

### Table

```{r}
#| label: NP summary table

np_summ %>%
  group_by(phase) %>%
  summarise(
    total_tested = sum(total_tested),
    total_grew = sum(total_grew),
    total_res = sum(total_res),
    n_na_res = sum(n_na_res),
    n = sum(n)
  ) %>%
  kable(
    col.names = c("Phase", "Total Tested", "Total Grew", "Total Resistant", "No Growth", "Total Villages"),
    caption = "Summary of NP samples across all villages"
  )

np_summ %>%
  dplyr::select(phase, arm, total_tested, total_grew, total_res, n_na_res, n) %>%
  kable(
    col.names = c("Phase", "Arm", "Total Tested", "Total Grew", "Total Resistant", "No Growth", "Total Villages"),
    caption = "Summary of NP samples by treatment arm"
  ) %>%
  kable_styling(full_width = FALSE, position = "left")

```

### Boxplot

```{r}
#| label: NP boxplot
#| fig-width: 8

np_summ_plot <- np_summ %>%
  mutate(txt = paste0("Total tested: ", total_tested, 
                      "\nTotal grew: ", total_grew, 
                      "\nTotal resistant: ", total_res,
                      # "\nOverall proportion resistant (of those that grew): ", round(overall_prop_res, 3),
                      # "\nOverall proportion resistant (of those tested): ", round(overall_prop_res_test, 3),
                      "\n\nTotal villages: ", n,
                      "\n0 grew in: ", n_na_res, " (", round(100*n_na_res/n, 1), "%)"),
         txt2 = paste0("Total villages: ", n,
                      "\n0 grew in: ", n_na_res, " (", round(100*n_na_res/n, 1), "%)")) %>%
  mutate(y = ifelse(arm == "azithro", 10, 5.5),
         y2 = ifelse(arm == "azithro", 1, 0.75))
  

ggplot(np_dat) +
  geom_boxplot(aes(x = arm, y = prop_res, color = arm, fill = arm), alpha = 0.3) +
  geom_jitter(aes(x = arm, y = prop_res, color = arm), width = 0.1, alpha = 0.5) +
  geom_text(
    data = np_summ_plot,
    aes(
      x = arm,
      y = 1,
      label = txt2,
      color = arm
    ),
    hjust = 0.5,
    vjust = 1,
    size = 3
  ) +
  theme_minimal(base_size = 14) +
  labs(
    title = "Boxplot of Proportion Resistant in NP Samples",
    x = "Treatment Arm",
    y = "Proportion Resistant"
  ) +
  facet_wrap(~phase) +
  scale_color_manual(values = c("azithro" = "#f1a226", "placebo" = "#003f5c")) +
  scale_fill_manual(values = c("azithro" = "#f1a226", "placebo" = "#003f5c")) +
  theme(legend.position = "bottom") +
  ylim(0, 1) 

```

### Map

```{r}
#| label: NP summary map
#| fig-width: 9

np_plot_map <- np_dat %>%
  mutate(zero_growth = ifelse(n_grew == 0, TRUE, FALSE)) %>%
  left_join(morb_gps, by = "grappe") %>%
  st_as_sf(coords = c("longitude", "latitude"), crs = global_crs, remove = FALSE) 

ggplot() +
  geom_sf(data = niger_shp %>% filter(mordor_states), fill = "white", color = "black", alpha = 0.5) +
  geom_sf(data = subset(np_plot_map, zero_growth == FALSE), aes(color = arm, size = prop_res), shape = 16, alpha = 0.7) +
  geom_sf(data = subset(np_plot_map, zero_growth == TRUE), aes(color = arm), shape = 2, alpha = 0.7) +
  scale_color_manual(values = c("azithro" = "#f1a226", "placebo" = "#003f5c"), name = "Arm") +
  theme_minimal(base_size = 14) +
  labs(
    title = "Map of Proportion Resistant in NP Samples at 24 Months",
    subtitle = "Hollow triangles indicate villages with zero growth"
  ) +
  theme(legend.position = "bottom") +
  facet_wrap(~phase) +
  guides(x = "none", y = "none") +
  scale_size_continuous(name = "Proportion Resistant", range = c(1, 10), limits = c(0, 1))

```

# Correlation between tx intensity and resistance in NP samples

```{r}
#| label: Estimate correlation between treatment intensity and resistance

np_tx_int <- np_dat %>%
  left_join(morb_tx_int %>% dplyr::filter(idw_power == 1), by = c("grappe", "arm"), relationship = "many-to-many") %>%
  mutate(zero_growth = ifelse(n_grew == 0, TRUE, FALSE))

np_corr <- np_tx_int %>%
  group_by(arm, phase, tx_type) %>%
  summarise(cor = unname(cor.test(tx_int, prop_res, method = "spearman", na.action(na.exclude))$estimate),
            n = n()-sum(zero_growth)) %>%
  ungroup()

np_perm <- perm_tx_int_raw %>% 
  dplyr::filter(idw_power == 1) %>%
  left_join(np_dat, by = c("grappe"), relationship = "many-to-many") %>%
  mutate(zero_growth = ifelse(n_grew == 0, TRUE, FALSE))

np_perm_corr <- np_perm %>%
  group_by(perm_id, arm, phase, tx_type) %>%
  summarise(cor = unname(cor.test(tx_int, prop_res, method = "spearman", na.action(na.exclude))$estimate),
            n = n()-sum(zero_growth)) %>%
  ungroup()

```

```{r}
#| label: Permutation test

np_cor_lookup <- np_corr %>%
  dplyr::select(arm, phase, tx_type, cor) %>%
  {setNames(split(., seq(nrow(.))), 
            paste(.$arm, .$phase, .$tx_type, sep = "_"))}

np_perm_dists <- np_perm_corr %>%
  mutate(lookup_key = paste(arm, phase, tx_type, sep = "_")) %>%
  group_split(lookup_key, .keep = TRUE) 

np_corr_pvals <- mclapply(np_perm_dists, function(group_data) {
  tryCatch({
    key <- unique(group_data$lookup_key)
    obs_data <- np_cor_lookup[[key]]
    obs_rho <- obs_data$cor

    rho_pval <- tryCatch({
      get_two_sided_pval(obs = obs_rho, empirical_dist = group_data$cor)
    }, error = function(e) NA_real_)
    
    tibble(
      arm = obs_data$arm[1],
      phase = obs_data$phase[1], 
      tx_type = obs_data$tx_type[1],
      rho = obs_rho,
      perm_p = rho_pval
    )
  }, error = function(e) {
    warning(paste("Error processing group:", e$message))
    # Return a row with NAs even when there's an error
    tibble(
      arm = group_data$arm[1],
      phase = group_data$phase[1], 
      tx_type = group_data$tx_type[1],
      rho = obs_rho,
      perm_p = NA_real_
    )
  })
}, mc.cores = n_cores) %>%
  bind_rows()

# Add observed values to the results

np_corr <- np_corr %>%
  rename(rho = cor) %>%
  left_join(np_corr_pvals, 
            by = c("arm", "phase", "tx_type", "rho"))

saveRDS(np_corr, here("data", "output", "np_corr.RDS"))

```

## Correlation results

```{r}
#| label: Correlation results table

np_corr %>%
  mutate(exposure = ifelse(tx_type == "azithro", "Primary exposure", "NCE")) %>%
  dplyr::select(-tx_type) %>%
  arrange(exposure, phase, arm) %>%
  mutate(rho = round(rho, 3),
         perm_p = round(perm_p, 3)) %>%
  dplyr::select(exposure, phase, arm, n, rho, perm_p, n) %>%
  kable(
    col.names = c("Exposure", "Phase", "Arm", "N (excluding zero growth)", "Spearman's rho", "Permutation p-value"),
    caption = "Correlation between Treatment Intensity and Proportion Resistant in NP Samples"
  ) %>%
  kable_styling(full_width = FALSE, position = "left")

```

### Scatterplots

```{r}
#| label: Scatterplot of correlation

y_axis_title <- "Proportion of nasopharyngeal<br>*S. pneumoniae* with macrolide resistance"

np_fig_txt <- np_corr %>%
  mutate(plot_label = paste0(
    'rho == ', sprintf("%.2f", rho), 
    ' * "," ~ italic(p) == ', sprintf("%.2f", perm_p), 
    ' * ";" ~ N == ', n
  ),
    y = ifelse(arm == "azithro", 0.9, 0.8),
  y_perm = ifelse(arm == "azithro", 10, 8)
  )

tx_type_names <- c(`azithro` = "Primary exposure", `placebo` = "NCE")

ggplot(data = np_tx_int, aes(x = tx_int, y = prop_res, color = arm)) +
  geom_point(alpha = 0.5) +
  geom_text(data = np_fig_txt, 
            aes(y = y, color = arm, label = plot_label), 
            x = 1,
            hjust = 1,
            parse = TRUE,
            show.legend = FALSE) +
  theme_minimal(base_size = 14) +
  facet_grid(tx_type ~ phase, labeller = labeller(tx_type = tx_type_names)) +
  theme(legend.position = "bottom",
        panel.spacing = unit(0.75, "cm"),
        axis.title.y = ggtext::element_markdown()) +
  scale_y_continuous(limits = c(0, 1),
                     name = y_axis_title) +
  scale_x_continuous(limits = c(0, 1),
                     name = "Geographic treatment intensity") +
  scale_color_manual(
    name = "Monitoring village treatment",
    breaks = c("azithro", "placebo"),
    labels = c("Azithromycin", "Placebo"),
    values = arms_colors
  ) + 
  annotate("text", x = 0.5, y = 0.5, label = "NOT REAL DATA",
             hjust = 0.5, vjust = 0.5, col = "grey", cex = 16,
             fontface = "bold", alpha = 0.5, angle = 30)

```

```{r}
#| label: Supplementary figure plot
#| fig-width: 6
#| fig-height: 8

y_axis_title_fig <- "Proportion of nasopharyngeal *S. pneumoniae* with macrolide resistance"

panelA <- ggplot(data = subset(np_tx_int, phase == "24 months" & tx_type == "azithro"), 
       aes(x = tx_int, y = prop_res, color = arm)) +
  geom_point(size = 3.5,
             alpha = 0.6) +
  geom_text(data = subset(np_fig_txt, phase == "24 months" & tx_type == "azithro"), 
            aes(y = y, color = arm, label = plot_label), 
            x = 1,
            size = 5,
            hjust = 1,
            parse = TRUE,
            show.legend = FALSE) +
  theme_minimal(base_size = 14) +
  theme(legend.position = "bottom", axis.title.y = ggtext::element_markdown()) +
  scale_y_continuous(limits = c(0, 1),
                     name = y_axis_title_fig) +
  scale_x_continuous(limits = c(0, 1),
                     name = "Geographic treatment intensity of azithromycin") +
  scale_color_manual(
    name = "Monitoring village treatment",
    breaks = c("azithro", "placebo"),
    labels = c("Azithromycin", "Placebo"),
    values = arms_colors
  ) +
  ggtitle("A") + 
  annotate("text", x = 0.5, y = 0.5, label = "NOT REAL DATA",
             hjust = 0.5, vjust = 0.5, col = "grey", cex = 16,
             fontface = "bold", alpha = 0.5, angle = 30)

panelB <- ggplot(data = subset(np_tx_int, phase == "24 months" & tx_type == "placebo"), 
       aes(x = tx_int, y = prop_res, color = arm)) +
  geom_point(size = 3.5,
             alpha = 0.6) +
  geom_text(data = subset(np_fig_txt, phase == "24 months" & tx_type == "placebo"), 
            aes(y = y, color = arm, label = plot_label), 
            x = 1,
            size = 5,
            hjust = 1,
            parse = TRUE,
            show.legend = FALSE) +
  theme_minimal(base_size = 14) +
  theme(legend.position = "bottom", axis.title.y = ggtext::element_markdown()) +
  scale_y_continuous(limits = c(0, 1),
                     name = y_axis_title_fig) +
  scale_x_continuous(limits = c(0, 1),
                     name = "Geographic treatment intensity of placebo") +
  scale_color_manual(
    name = "Monitoring village treatment",
    breaks = c("azithro", "placebo"),
    labels = c("Azithromycin", "Placebo"),
    values = arms_colors
  ) +
  ggtitle("B") + 
  annotate("text", x = 0.5, y = 0.5, label = "NOT REAL DATA",
             hjust = 0.5, vjust = 0.5, col = "grey", cex = 16,
             fontface = "bold", alpha = 0.5, angle = 30)

supp_fig_np <- panelA / panelB +
    # plot_annotation(tag_levels = 'A') +
  plot_layout(guides = "collect", axes = "collect_y") & theme(legend.position = "bottom")

supp_fig_np

ggsave(supp_fig_np, filename = here("figs", "manuscript", "supp-figs", "supp_fig8-np.png"), 
       width = 6, height = 8, dpi = 600, bg = "white")

```

**Supplementary figure 8**: Relationship between geographic treatment
intensity and the proportion of nasopharyngeal S. pneumoniae that were
macrolide-resistant at 24 months.

A. Relationship between the azithromycin treatment intensity and the
village-level proportion of S. pneumoniae, isolated from nasopharyngeal
swabs, that was resistant to erythromycin at 24 months, estimated as
Spearman rank-order correlations (ρ). Points represent anti-microbial
resistance (AMR) monitoring villages, with azithromycin-treated villages
in yellow and placebo-treated villages in blue.

B. Relationship between the placebo treatment intensity (negative
control exposure) and the proportion of S. pneumoniae that was resistant
to erythromycin at 24 months.

The sample size, N, is the number of villages in which pneumococcus was
isolated from at least one of the children sampled and were therefore
included in the correlation calculation. All p-values are two-sided and
derived from a permutation test.

### Permutation distributions

```{r}
#| label: Permutation distributions

perm_combined <- bind_rows(np_perm_dists)

ggplot(perm_combined, aes(x = cor, color = arm, fill = arm)) +
  geom_vline(xintercept = 0, color = "black", linewidth = 0.3) +
  geom_density(alpha = 0.3) +
  geom_vline(data = np_corr, 
             aes(xintercept = rho, color = arm),
             linetype = "dotted",
             linewidth = 0.8) +
  geom_label(data = np_fig_txt, 
            aes(y = y_perm, color = arm, label = plot_label), 
            x = 1,
            hjust = 1,
            vjust = 1,
            parse = TRUE,
            show.legend = FALSE,
            fill = "white") +
  facet_grid(tx_type ~ phase,
             labeller = labeller(tx_type = tx_type_names)) +
  scale_x_continuous(name = "Spearman Correlation", limits = c(-1, 1)) +
  scale_y_continuous(name = "Density", limits = c(0, 10)) +
  scale_color_manual(
    name = "Monitoring village treatment",
    breaks = c("azithro", "placebo"),
    labels = c("Azithromycin", "Placebo"),
    values = arms_colors
  ) +
  scale_fill_manual(
    name = "Monitoring village treatment",
    breaks = c("azithro", "placebo"),
    labels = c("Azithromycin", "Placebo"),
    values = arms_colors
  ) +
  labs(
    title = "Permutation Null Distributions with Observed Correlations"
  ) +
  theme_minimal(base_size = 14) +
  theme(
    legend.position = "bottom",
    panel.spacing = unit(1, "lines")
  ) + 
  annotate("text", x = 0, y = 1.5, label = "NOT\nREAL\nDATA",
             hjust = 0.5, vjust = 0.5, col = "darkgrey", cex = 12,
             fontface = "bold", alpha = 0.5)


```
